---
title: "Fall 2023 Workshop Survey Responses"
author: "Seth Erickson"
date: 2024-03-03
editor: visual
format: 
   html:
     df-print: kable
---

## Combined Workshop Survey Responses

```{r}
#| message: false
library("tidyverse")

# list of workshop IDs to filter results
workshops <- c("2023-10-23-ucsb-git",
               "2023-11-14-ucsb-python")

results <- read_csv("data-joined/all_workshops.csv") %>% 
  filter(workshop %in% workshops)
```

## Departments

```{r}
results %>% select(dept_select.pre) %>% 
  separate_rows(dept_select.pre, sep=",") %>% 
  group_by(dept_select.pre) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
```

### "Other" Departments

```{r}
results %>% 
  group_by(dept_other.pre) %>% 
  summarise(count=n()) %>%
  arrange(desc(count))
```

## Occupation

```{r}
results %>% select(occupation.pre) %>% 
  separate_rows(occupation.pre, sep=",") %>% 
  group_by(occupation.pre) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
```

## Motivations

```{r}
results %>% select(motivation_select.pre) %>% 
  separate_rows(motivation_select.pre, sep=",") %>% 
  group_by(motivation_select.pre) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
```

## Hopes

```{r}
results %>% group_by(workshop) %>% 
  select(workshop, hopes.pre) %>% 
  drop_na()
```

## Applying the material

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_apply.post) %>% 
  select(workshop, agree_apply.post) %>% 
  drop_na() %>%
  summarize(count=n())

```

## Comfortable in the workshop environment

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_comfortable.post) %>% 
  select(workshop, agree_comfortable.post) %>% 
  drop_na() %>%
  summarize(count=n())
```

## Got clear answers

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_clearanswers.post) %>% 
  select(workshop, agree_clearanswers.post) %>% 
  drop_na() %>%
  summarize(count=n())
```

## Instructors were enthusiastic

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_instr_enthusiasm.post) %>% 
  select(workshop, agree_instr_enthusiasm.post) %>% 
  drop_na() %>%
  summarize(count=n())
```

## Comfortable interacting with instructors

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_instr_interaction.post) %>% 
  select(workshop, agree_instr_interaction.post) %>% 
  drop_na() %>%
  summarize(count=n())
```

## Instructors were knowledgeable

```{r}
#| message: false
results %>% 
  group_by(workshop, agree_instr_knowledge.post) %>% 
  select(workshop, agree_instr_knowledge.post) %>% 
  drop_na() %>%
  summarize(count=n())
```

## Instructor interaction example

```{r}
#| message: false
results %>% 
  group_by(workshop) %>% 
  select(workshop, instructor_example.post) %>%
  drop_na()
```

## Workshop Strengths

```{r}
results %>% 
  group_by(workshop) %>% 
  select(workshop, workshop_strengths.post) %>% 
  drop_na()
```

## Ways to improve the workshop

```{r}
results %>% 
  group_by(workshop) %>% 
  select(workshop, workshop_improved.post) %>% 
  drop_na()
```

## Topic Suggestions

```{r}
results %>% 
  group_by(workshop) %>% 
  select(workshop, suggest_topics.post) %>% 
  drop_na()
```
