---
title: "Spring 2024 Containers Workshop Survey Responses"
author: "Jose Niño Muriel"
date: 2024-06-17
editor: visual
format: 
   html:
     code-fold: true
     df-print: kable
---

## Number of responses
```{r}
#| message: false
library("tidyverse")

# list of workshop IDs to filter results
workshops <- c("2024-06-04-ucsb-containers")

results <- read_csv("data-joined/all_workshops.csv") %>% 
  filter(workshop %in% workshops)

pre_survey <- results %>%
  select(ends_with(".pre"))

post_survey <- results %>%
  select(ends_with(".post"))

n_pre <- sum(apply(post_survey, 1, function(row) all(is.na(row))))
n_post <- sum(apply(pre_survey, 1, function(row) all(is.na(row))))

```

Total responses: `{r} nrow(results)`

Responded only pre-workshop survey: `{r} n_pre`

Responded only post-workshop survey: `{r} n_post`

Responded both pre- and post-: `{r} nrow(results) - n_pre - n_post`

## Departments

```{r}
results %>% select(dept_select.pre) %>% 
  separate_rows(dept_select.pre, sep=",") %>% 
  group_by(dept_select.pre) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
```

### "Other" Departments

```{r}
results %>% 
  group_by(dept_other.pre) %>% 
  summarise(count=n()) %>%
  arrange(desc(count))
```

## Current occupation / Career stage

```{r}
results %>% select(occupation.pre) %>% 
  separate_rows(occupation.pre, sep=",") %>% 
  group_by(occupation.pre) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
```

## Motivation - Why are you participating in this workshop?

```{r}
results %>% select(motivation_select.pre) %>% 
  separate_rows(motivation_select.pre, sep=",") %>% 
  group_by(motivation_select.pre) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
```

## How did you find out about this workshop?

```{r}
results %>% select(findout_select.pre) %>% 
  separate_rows(findout_select.pre, sep=",") %>% 
  group_by(findout_select.pre) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
```

## What you most hope to learn?

```{r}
results %>% group_by(workshop) %>% 
  select(workshop, hopes.pre) %>% 
  drop_na()
```

## Can immediatly apply what they learned

```{r}
#| message: false
#| echo: false
#| output: false
orderedq <- c("Strongly Disagree", "Somewhat Disagree", "Neither Agree or Disagree","Somewhat Agree", "Strongly Agree")
addNA(orderedq)
```
```{r}
#| message: false
results <- results %>%
  mutate(
    across(
      c(agree_apply.post, agree_comfortable.post, agree_clearanswers.post, agree_instr_enthusiasm.post, agree_instr_interaction.post, agree_instr_knowledge.post),
      function(x) factor(x, levels = orderedq, ordered = TRUE
      )
    )
  )

results %>% 
  group_by(workshop,agree_apply.post) %>% 
  select(workshop, agree_apply.post) %>% 
  summarize(count=n()) %>%
  ungroup() %>%
  drop_na() %>%
  complete(workshop, agree_apply.post, fill = list(count = 0)) %>%
  arrange(agree_apply.post)
```

## Comfortable learning in the workshop environment

```{r}
#| message: false

results %>% 
  group_by(workshop,agree_comfortable.post) %>% 
  select(workshop, agree_comfortable.post) %>% 
  summarize(count=n()) %>%
  ungroup() %>%
  drop_na() %>%
  complete(workshop, agree_comfortable.post, fill = list(count = 0)) %>%
  arrange(agree_comfortable.post)
```

## Got clear answers from instructors

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_clearanswers.post) %>% 
  select(workshop, agree_clearanswers.post) %>% 
  summarize(count=n()) %>%
  ungroup() %>%
  drop_na() %>%
  complete(workshop, agree_clearanswers.post, fill = list(count = 0)) %>%
  arrange(agree_clearanswers.post)
```

## Instructors were enthusiastic

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_instr_enthusiasm.post) %>% 
  select(workshop, agree_instr_enthusiasm.post) %>% 
  summarize(count=n()) %>%
  ungroup() %>%
  drop_na() %>%
  complete(workshop, agree_instr_enthusiasm.post, fill = list(count = 0)) %>%
  arrange(agree_instr_enthusiasm.post)
```

## Comfortable interacting with instructors

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_instr_interaction.post) %>% 
  select(workshop, agree_instr_interaction.post) %>% 
  summarize(count=n()) %>%
  ungroup() %>%
  drop_na() %>%
  complete(workshop, agree_instr_interaction.post, fill = list(count = 0)) %>%
  arrange(agree_instr_interaction.post)
```

## Instructors were knowledgeable about the material

```{r}
#| message: false
results %>% 
  group_by(workshop,agree_instr_knowledge.post) %>% 
  select(workshop, agree_instr_knowledge.post) %>% 
  summarize(count=n()) %>%
  ungroup() %>%
  drop_na() %>%
  complete(workshop, agree_instr_knowledge.post, fill = list(count = 0)) %>%
  arrange(agree_instr_knowledge.post)
```

## How an instructor or helper affected your learning experience

```{r}
#| message: false
results %>% 
  group_by(workshop) %>% 
  select(workshop, instructor_example.post) %>%
  drop_na()
```

## Workshop Strengths

```{r}
results %>% 
  group_by(workshop) %>% 
  select(workshop, workshop_strengths.post) %>% 
  drop_na()
```

## Ways to improve the workshop

```{r}
results %>% 
  group_by(workshop) %>% 
  select(workshop, workshop_improved.post) %>% 
  drop_na()
```


## How likely are you to recommend this workshop? Scale 0 - 10
```{r}
tapply(results$recommende_score.post, results$workshop, summary)
```



## Topic Suggestions

```{r}
results %>% 
  group_by(workshop) %>% 
  select(workshop, suggest_topics.post) %>% 
  drop_na()
```
